How kids code and how we know it:\\An exploratory study in the Scratch project repository

### 2016-04-18 Paper/paper.tex
From 4 to 3 research questions

\newcommand{\nPrograms}{250.166}
\newcommand{\nemptyPrograms}{14.285}
\newcommand{\nScriptPrograms}{233.513}
\newcommand{\nProgramsWithClones}{67.177}
\newcommand{\dup}{\emph{Duplication}~}

@@

\begin{itemize}
\item[RQ1] What are the size and complexity characteristics of Scratch programs?
\item[RQ2] Which coding abstractions and programming concepts and features are commonly used when programming in the Scratch environment?
\item[RQ3] How are coding style conventions applied in Scratch?
\item[RQ4] Which code smells and bad programming practices are common in Scratch programs?
\end{itemize}

@@

\textbf{RQ2} Which coding abstractions and programming concepts and features are commonly used when programming in the Scratch environment? Using the code in the dataset, we perform a detailed statistical analysis of code characteristics to answer RQ2 (Section ??)

\textbf{RQ3} How are coding style conventions applied in Scratch? to examine if coding style conventions are used, we qualitatively analyze..

\textbf{RQ4} Which code smells and bad programming practices are common in Scratch programs?

@@

\subsection{Program size and complexity}
Size -per Project:sprites, blocks and locs, events/triggers
nestendness	
cyclomatic complexity

@@

\subsection{Coding style}
naming -functions, sprites, variables
positioning - overlapping /visibility

@@

>>>>

\newcommand{\nPrograms}{250.166}
\newcommand{\nemptyPrograms}{14.285}
\newcommand{\nScriptPrograms}{233.491}
\newcommand{\nProgramsWithClones}{67.177}
\newcommand{\dup}{\emph{Duplication}~}

@@

\begin{itemize}
\item[RQ1] What are the size and complexity characteristics of Scratch programs?
\item[RQ2] Which coding abstractions and programming concepts and features are commonly used when programming in the Scratch environment?
\item[RQ3] How common are code smells and bad programming practices in Scratch programs?
\end{itemize}

@@

\textbf{RQ2} Which coding abstractions and programming concepts and features are commonly used when programming in the Scratch environment? Using the code in the dataset, we perform a detailed statistical analysis of code characteristics to answer RQ2 (Section ??). We manually assigned types to commands/blocks.

\textbf{RQ3} Which code smells and bad programming practices are common in Scratch programs?  to examine if coding style conventions are used, we qualitatively analyze..

@@

\subsection{Program size and complexity}
Size -per Project:sprites, blocks and locs, events/triggers
lines in stage/sprites/procedures
nestendness	
cyclomatic complexity

lines do not count the ending line of enclosures
only sprites with code are counted
indentation: 1 for top-level, for nested (rest-1)/2 (goes 1,3,5, etc), for others normal

@@

@@

coding style -naming -functions, sprites, variables
code block positioning - overlapping /visibility
